Language-Based Security for Low-Level MPC

### 2024-09-02 ppdp24/slides.tex
checkpoint

  \begin{itemize}
  \item Messages $\mx{ss1}$ through $\mx{ss3}$ are \emph{not} probabilistically independent of inputs
    secrets, but ...
  \item They \emph{are} independent of secrets conditioned on the output!
  \end{itemize}

@@

  The output phase does not reveal additional information, but is
  algebraically correct.
  \begin{block}{Client Outputs}
    $$
    \begin{array}{lll}
      \out{1} &:=& \elab{(\mesg{ss1} \fplus \mesg{ss2} + \mesg{ss3})}{1}\\
      \out{2} &:=& \elab{(\mesg{ss1} \fplus \mesg{ss2} + \mesg{ss3})}{2}\\
      \out{3} &:=& \elab{(\mesg{ss1} \fplus \mesg{ss2} + \mesg{ss3})}{3}
    \end{array}
    $$
  \end{block}

>>>>

  \begin{itemize}
  \item Messages $\mx{ss1}$ through $\mx{ss3}$ are \emph{not} probabilistically independent of inputs, but ...
  \item They \emph{are} independent of secrets conditioned on the output! 
  \end{itemize}

@@

  \begin{alertblock}
    Any $\mx{ss1}{*},\mx{ss2}{*},\mx{ss3}{*}$ such that:
    $$
    \mx{ss1}{*} + \mx{ss2}{*} + \mx{ss3}{*} = \sx{1}{1} + \sx{2}{2}  + \sx{3}{3}
    $$
    are \cemph{equally likely}.
  \end{alertblock}
  The output phase does not reveal additional information, but is
  algebraically correct.
  \begin{block}{Client Outputs}
    $$
    \begin{array}{lll}
      \out{1} &:=& \elab{(\mesg{ss1} \fplus \mesg{ss2} + \mesg{ss3})}{1}\\
      \out{2} &:=& \elab{(\mesg{ss1} \fplus \mesg{ss2} + \mesg{ss3})}{2}\\
      \out{3} &:=& \elab{(\mesg{ss1} \fplus \mesg{ss2} + \mesg{ss3})}{3}
    \end{array}
    $$
  \end{block}
